---
title: "Simple document"
author: "Ze Li"
date: "2023-09-12"
output: 
  html_document: 
   toc: true
   toc_float: true
   code_folding: hide
---

```{r library, echo = FALSE, message = FALSE}
library(tidyverse)
# echo=FALSE hide this code chunk
# message = FALSE hide result of code chunk
# eval = FALSE show code but not run it
```


I'm an R Markdown document! 

# Section 1 First code chunk

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r samp norm}
samp = rnorm(100)
length(samp)
```

The mean of the sample is `r round(mean(samp), digits = 4)`

# Section 2 Make a plot

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

This code is borrowed from last lecture; it creates a dataframe for plotting.

```{r df}
plot_df = 
  tibble(
    x = rnorm(1000,sd=0.5),
    y = 1 + 2*x + rnorm(1000)
  )
```

Next up is a histogram of the `x` variable in `plot_df`.

```{r hist}
ggplot(plot_df, aes(x=x)) + geom_histogram()
```

Lastly, I'll do a scatter plot.

```{r scatter}
ggplot(plot_df, aes(x=x,y=y)) + geom_point()
```

here's a list:

* this is the first list thing
* here's another list item

# Section 3: Learning assessment

Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. 

Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE?

```{r la_df}
la_df = 
  tibble(
    num_samp = rnorm(500,mean = 1),
    log_vec = num_samp > 0,
    absnum_vec = abs(rnorm(500,mean = 1))
  )
ggplot(la_df, aes(x=absnum_vec)) + geom_histogram()
```

# Section 4: Text formatting examples

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell

# Section 5: New Workflow
```{r}
# output: word_document
# output: pdf_document
# output: github_document
```

